### 2013-12-14 paper/paper.tex
blerg^blerg

In this paper, we discuss our development of a model which attempts to predict the bugginess of commits submitted to a repository using machine-learning techniques. This tool furthers the goal of better directing the testing efforts of repository owners by providing recommendations about which commits are most likely to be buggy. The next section frames this project with the related work of others. Section [CITE] discusses our approach in developing our model including data sources, feature selection, and algorithm development. Section [CITE] discusses the refinement of the model, presents our results, and discusses our methodology for validation of our results. Section [CITE] discusses shortcomings, threats to validity, and future work, and section [CITE] concludes.

\section{Related Work}
Using version control system history to aid the development process is not a new idea;  the wealth of data that repositories store makes them very attractive artifacts to researchers who want to understand and improve the ways in which code is written.  In the last ten years a good deal of work has gone into trying to use repository data to make various aspects of the development process easier [3]. In the early 2000s Zimmerman et al [1] and Ying [2] developed systems to mine version history to make suggestions on potential locations to make changes based on recent alterations to versioned files. Their results were very interesting, reliably finding associations between sections of code and between code and documentation.

A common goal in many projects involving software repositories is attempting to predict the bugginess of future code using some set of metrics. A wide variety of metrics have been researched, including code churn [6], association of changed files, distance between team members [7], and commit size[8]. Recent research has also been done to analyze the accuracy of predicting one repository’s future defects using a different repository’s past history [12].   Work has also been done on analyzing characteristics of bugs and bug fixes[9] [10]

@@

Some work has also been done by this group at attempting to use machine learning techniques to predict the bugginess of future commits.  Our work differs from theirs in several ways, namely that their work focuses much more heavily on analysis of committed code, which we generally ignore in favor of the attributes and message of a commit.    
\section{Approach}
\subsection{Mining Git Repositories}
We mined eight open-source repositories hosted on Github.com for features to serve as our testing data sets (Table CITE). The repositories are quite varied; they range in size from around 2000-30000 commits and in age from roughly 3-13 years. The repositories also vary considerably in their goals — they include a programming language, a versioning control system, and a nuclear fuel cycle simulator. We extracted two sets of features about commits from each repository: commit attributes and message attributes. Commit attributes are information about a commit excluding actual analysis of the code or the commit message. Examples of commit attributes we extracted are the number of lines added, the number of lines removed, the contributor, the length of the comment, the day of the week of the commit, and the number of files altered. The commit message attributes we selected are the frequency of words, grammatical correctness, and readability and stylistic metrics of the message. We used the Kincaid metric for readability [CITE], diction, a unix command line tool, to quantify style (triteness, over-wordiness) [CITE], and Queequeg to test the degree of grammatical correctness [CITE] for each commit message. Our analysis of the commit messages assumes they are written in English. A complete list of attributes examined can be found in Table [CITE].

@@

\section{Results}
\subsection{Feature Analysis}
We went through several iterations of features to represent commits; we will briefly touch here on the features that did not work well before continuing to a more lengthy discussion of the features we actually used.  Our first attempt at classifying commits attempted to cast this prediction problem as equivalent to catching email spam.  A simple way to predict that an email is spam is to train on the individual words in spam emails.  The more a word is associated with being seen only in spam email, the more likely an email containing that word is spam.  We attempted to apply this to commits by training a Naive Bayes classifier on the words of a commit messages. This turned out to not be a very good idea, with results about as good as randomly guessing clean or buggy.  Abandoning the buggy commit as email spam metaphor, we decided to look at attributes of the commit.

@@

To test the effectiveness of our feature selection, we mined features from eight open source repositories.  We attempted to choose projects with different life spans and applications to make our results more generalizable.  The list of projects mined, their number of commits, and the percentage of those commits we found to be buggy are in table {CITE}.  
\begin{table}
\begin{center}
    \begin{tabular}{ | c | c | c | c | c |}
    \hline
    Repository & Start Date & $\#$  Commits & $\#$ Buggy  Commits & \% Buggy \\ \hline
    one     & June 2008   &   8179 & 2744 & 33.6 \\ \hline
    cyclus & March 2010 &  2162 & 1071 & 49.5 \\ \hline
    git        & April 2005    &   28788 & 10682 & 37.1 \\ \hline
    jedit &Sept 1998 &  6890 & 3190 & 46.3 \\ \hline
    jquery     & March 2006   &   5608 & 3074 & 54.8 \\ \hline
    puppet & April 2005 &  12174 & 4812 & 39.5 \\ \hline
    scala     & Feb 2003   &   20398 & 9584 & 47.0 \\ \hline
    scipy & Feb 2001 &  10035 & 3252 & 32.4 \\ \hline        	
    \end{tabular}
\end{center}\caption{Mined Repositories}
\label{tab:repos}
\end{table}

@@

For training data, we took commits from the final day of 2012 back six months, one year, two years, and to the start of the repository.  The goal here is to see how our results change with more data to train on (and potentially overfit to).  Tables [CITE] and [CITE] show the size and percentage of commits which are buggy respectively.  Notice as time increases, the percentage of buggy commits increases (excepting scala all time).  This seems to be an artifact of our heuristic; older bugs are more likely to have associated bug fixes, and so are more likely to be found by our method.  Without having the actual distribution of buggy commits, we can make no assumptions about its trend over time.

@@

one  & 23.1 & 26.4 & 30.2 & 35.4 & 37.7 \\ \hline 
cyclus  & 30.6 & 44.4 & 50.6 & 54.9 & 55.9 \\ \hline 
git  & 13.9 & 22.1 & 22.5 & 23.4 & 39.7 \\ \hline
jedit  & 6.7 & 13.9 & 24.7 & 23.1 & 47.3 \\ \hline
jquery  & 35.7 & 43.2 & 46.6 & 53.9 & 58.6 \\ \hline 
puppet  & 18.7 & 20.0 & 26.1 & 29.1 & 44.1 \\ \hline 
scala  & 27.2 & 45.3 & 48.8 & 50.3 & 48.9 \\ \hline 
scipy  & 18.8 & 23.6 & 23.6 & 24.7 & 35.5 \\ \hline
\end{tabular}
\end{center}\caption{Bugginess of Training and Test Sets}
\label{tab:buggy}
\end{table}

@@

To compare our features against some baseline, we created a “random weighted coin” classifier which calculated the percent buggy in a training set, and used this percentage as the weight on a random buggy/clean coin for each test instance.  We feel this represents a better floor against which to compare our results than simply using a fair coin.  To compare the effectiveness of attribute and message features, we also trained classifiers using only attribute features, only message features, and both sets of features.

@@

\end{figure}
Figure [CITE] contains our accuracy results using one year of training data.  Results for random coin vary but in general are about fifteen to twenty points lower than the rest of the classifiers.  Using attribute features only tends to work as well or slightly better than message features, with big drops only occurring in cyclus and jquery.  Using both sets of features is comparable to only using one, though it appears more similar to message attributes.

As much as we would like it to be otherwise, the 93.3 \% accuracy seen by jedit is more than a little misleading; the jquery test set is only 6.7\% buggy, and so the jedit classifiers simply guess clean for every instance. This is true for the majority of message-only feature classifiers; only cyclus and jquery classifiers ever classify any test commits as buggy.  The results from these classifiers are still promisingly higher than our baseline, which leads us to believe that our features do have some non-random correlation with clean and buggy commits.   All of our attribute-trained and attribute/message-trained classifiers have non-trivial decision boundaries.  To get a better idea of how well our classifiers actually are at correctly predicting commits as buggy, we examine precision/recall graphs for cyclus, scala (the two repositories with non-trivial decision boundaries) and scipy by varying the ensemble classifier threshold from 0.0\% agreement (always classify buggy) to 100\% agreement.

\begin{figure}[H]%
\centering
\subfloat[Cyclus]{\includegraphics[width=0.5\textwidth]{images/cyclus_pr}}\hfill%
\subfloat[Scala]{\includegraphics[width=0.5\textwidth]{images/scala_pr}}\\
\subfloat[Scipy]{\includegraphics[width=0.5\textwidth]{images/scipy_pr}}\hfill
\subfloat[Cyclus - ROC graph]{\includegraphics[width=0.5\textwidth]{images/cyclus_roc}}\hfill

@@

As these figures show, using only comments is better than random.  At the same time, using just comments performs worse in all cases than using attribute data.  Using attribute data performs about as well as training on both attribute and comment features.  This leads us to several conclusions.  First, both sets of attribute and comment features are more predictive than random.  Comparatively, attibute features are a much better approximation of a commit than comment features.  Combining attribute and comment features provide  little additional performance benefit over simply using attributes.

@@

 \begin{figure}[h]
\centering
	\subfloat[Accuracy]{\includegraphics[width=0.5\textwidth,height=0.3\textwidth]{images/time_comp}}\hfill
	\subfloat[Precision Recall Graph]{\includegraphics[width=0.5\textwidth]{images/time_pr}}\hfill

\caption{Training Data Size - Message and Attributes}
\label{git_comp}

\end{figure}
Accuracy across repositories tended to trend downward as the time frame from the training set increased.  Not visible in table [CITE] is the fact that for six months data sets, the likelihood  of trivial decision boundaries seems to increase.  On the other end of the spectrum, however,  it seems clear that using all of the data introduces too much noise.  Some of these projects predate git and almost certainly were originally in another version system.  Overall, it seems likely to us that recent commits are more representative of commits in the near future, which would explain the drop in results.  From our work, we suspect one to two years is the “optimal” range of sizes, though this will obviously be different for each repository, depending on how often they make commits.  We did not test this, but it might also be beneficial to allow a period of time between the training data and the most recent commit; this space could help reduce false negatives by allowing a reasonable amount of time for bug fixes for the training data to be added.

@@

A year of repository data before being able to use a tool seems like a fairly high price of admission.  Being able to substitute another repository’s history for your own with little to no hit in accuracy seems like it would make our tool more applicable.  Furthermore, what does this say about commits if commits from two unrelated repositories are similar enough that one can be used to train the other?  To answer these questions, we decided to use git’s commit history to train our classifier and test on the other seven repositories.  Scipy and git were chosen because they were large repositories with good performance and non trivial decision boundaries.  In order for training and testing data to be compatible, the user feature had to be removed from all data sets.

 \begin{figure}[h]
\centering
	\subfloat[Accuracy]{\includegraphics[width=0.5\textwidth,height=0.3\textwidth]{images/git_comp}}
	\subfloat[Precision Recall]{\includegraphics[width=.5\textwidth]{images/git_pr}}
\caption{Training With Git and Scipy - 1 Months, Message and Attribute Data}
\label{git_comp}

@@

In general, results tended to be comparable to those using their respective data sets.  The cross-repository classifier accuracies displayed the same trend of slow decrease as training data size increased, with a noticeable drop when all training data was used.

This comparable performance indicates to us that using a classifier trained on another repository is a valid proxy for repositories that do not have their own history.  It also seems that the distribution of message and commit attribute features we use do not vary much across repositories.  More work would need to be done to give such a claim actual weight, but if our features have global, general boundaries, could we use this information in some kind of prescriptive fashion, a la “keep your commits to X lines added if possible”. Or would knowledge and enforcement of this information simply shift the boundary?

\section{Threats to Validity}

@@

Our results have shown commits are not especially repository specific, but we believe they could potentially be user-specific?  Does it make more sense to have a user-specific classifier that examines the user’s commit history across the repositories they have contributed to than to have a single classifier that predicts labels for potentially many users. Studying this would not require much additional new work to be done beyond mining new repositories and organizing training sets.  If user-specifc commits are in fact better predictors of bugginess, additional work would need to be done to ensure user’s do not cherry-pick their training data to give an overly positive but invalid bias.

@@

\section{Concluding Remarks}

% references section

>>>>

In this paper, we discuss our development of a model which attempts to predict the bugginess of commits submitted to a repository using machine-learning techniques. This tool furthers the goal of better directing the testing efforts of repository owners by providing recommendations about which commits are most likely to be buggy. The next section frames this project with the related work of others. Section \ref{approach} discusses our approach in developing our model including data sources, feature selection, and algorithm development. Section \ref{results} discusses the refinement of the model, presents our results, and discusses our methodology for validation of our results. Section \ref{threats} discusses shortcomings, threats to validity, and future work, and section \ref{conclude} concludes our paper.

\section{Related Work}
Using version control system history to aid the development process is not a new idea;  the wealth of data that repositories store makes them very attractive artifacts to researchers who want to understand and improve the ways in which code is written.  In the last ten years a good deal of work has gone into trying to use repository data to make various aspects of the development process easier [CITE3]. In the early 2000s Zimmerman et al [CITE1] and Ying [CITE2] developed systems to mine version history to make suggestions on potential locations to make changes based on recent alterations to versioned files. Their results were very interesting, reliably finding associations between sections of code and between code and documentation.

A common goal in many projects involving software repositories is attempting to predict the bugginess of future code using some set of metrics. A wide variety of metrics have been researched, including code churn [6], association of changed files, distance between team members [CITE7], and commit size[CITE8]. Recent research has also been done to analyze the accuracy of predicting one repository’s future defects using a different repository’s past history [CITE12].   Work has also been done on analyzing characteristics of bugs and bug fixes[CITE9] [CITE10]

@@

Some work has also been done by this group at attempting to use machine learning techniques to predict the bugginess of future commits.  Our work differs from theirs in several ways, namely that their work focuses much more heavily on analysis of committed code, which we generally ignore in favor of the attributes and message of a commit.    
\section{Approach}
\label{approach}
\subsection{Mining Git Repositories}
We mined eight open-source repositories hosted on Github.com for features to serve as our testing data sets ; these can be seen in Table \ref{tab:repos}. The repositories are quite varied; they range in size from around 2000-30000 commits and in age from roughly 3-13 years. The repositories also vary considerably in their goals — they include a programming language, a versioning control system, and a nuclear fuel cycle simulator. We extracted two sets of features about commits from each repository: commit attributes and message attributes. Commit attributes are information about a commit excluding actual analysis of the code or the commit message. Examples of commit attributes we extracted are the number of lines added, the number of lines removed, the contributor, the length of the comment, the day of the week of the commit, and the number of files altered. The commit message attributes we selected are the frequency of words, grammatical correctness, and readability and stylistic metrics of the message. We used the Kincaid metric for readability [CITE], diction, a unix command line tool, to quantify style (triteness, over-wordiness) [CITE], and Queequeg to test the degree of grammatical correctness [CITE] for each commit message. Our analysis of the commit messages assumes they are written in English. A complete list of attributes examined can be found in Table [CITE].

@@

\section{Results}
\label{results}
\subsection{Feature Analysis}
We went through several iterations of features to represent commits; we will briefly touch here on the features that did not work well before continuing to a more lengthy discussion of the features we actually used.  Our first attempt at classifying commits attempted to cast this prediction problem as equivalent to catching email spam.  A simple way to predict that an email is spam is to train on the individual words in spam emails.  The more a word is associated with being seen only in spam email, the more likely an email containing that word is spam.  We attempted to apply this to commits by training a Naive Bayes classifier on the words of a commit messages. This turned out to not be a very good idea, with results about as good as randomly guessing clean or buggy.  Abandoning the buggy commit as email spam metaphor, we decided to look at attributes of the commit.

@@

To test the effectiveness of our feature selection, we mined features from eight open source repositories.  We attempted to choose projects with different life spans and applications to make our results more generalizable.  The list of projects mined, their number of commits, and the percentage of those commits we found to be buggy are in table \ref{tab:repos}.  
\begin{table}
\begin{center}
    \begin{tabular}{ | c | c | c | c | c |}
    \hline
    Repository & Startdate & $\#$  Commits & $\#$ Buggy  Commits & \% Buggy \\ \hline
    one     & June 2008   &   8179 & 2744 & 33.6 \\ \hline
    cyclus & March 2010 &  2162 & 1071 & 49.5 \\ \hline
    git        & April 2005    &   28788 & 10682 & 37.1 \\ \hline
    jedit & Sept 1998 &  6890 & 3190 & 46.3 \\ \hline
    jquery     & March 2006   &   5608 & 3074 & 54.8 \\ \hline
    puppet & April 2005 &  12174 & 4812 & 39.5 \\ \hline
    scala     & Feb 2003   &   20398 & 9584 & 47.0 \\ \hline
    scipy & Feb 2001 &  10035 & 3252 & 32.4 \\ \hline        	
    \end{tabular}
\end{center}\caption{Mined Repositories}
\label{tab:repos}
\end{table}

@@

For training data, we took commits from the final day of 2012 back six months, one year, two years, and to the start of the repository.  The goal here is to see how our results change with more data to train on (and potentially overfit to).  Tables \ref{tab:size} and \ref{tab:buggy} show the size and percentage of commits which are buggy respectively.  Notice as time increases, the percentage of buggy commits increases (excepting scala all time).  This seems to be an artifact of our heuristic; older bugs are more likely to have associated bug fixes, and so are more likely to be found by our method.  Without having the actual distribution of buggy commits, we can make no assumptions about its trend over time.

@@

one  & 23.1 & 26.4 & 30.2 & 35.4 & 37.7 \\ \hline 
cyclus  & 30.6 & 44.4 & 50.6 & 54.9 & 55.9 \\ \hline 
git  & 13.9 & 22.1 & 22.5 & 23.4 & 39.7 \\ \hline
jedit  & 6.7 & 13.9 & 24.7 & 23.1 & 47.3 \\ \hline
jquery  & 35.7 & 43.2 & 46.6 & 53.9 & 58.6 \\ \hline 
puppet  & 18.7 & 20.0 & 26.1 & 29.1 & 44.1 \\ \hline 
scala  & 27.2 & 45.3 & 48.8 & 50.3 & 48.9 \\ \hline 
scipy  & 18.8 & 23.6 & 23.6 & 24.7 & 35.5 \\ \hline
\end{tabular}
\end{center}\caption{Percent Bugginess of Training and Test Sets}
\label{tab:buggy}
\end{table}

@@

To compare our features against some baseline, we created a “random weighted coin” classifier which calculated the percent buggy in a training set, and used this percentage as the weight on a random buggy/clean coin for each test instance.  We feel this represents a better floor against which to compare our results than simply using a fair coin. All discussion of random coin results are the average of 100 trials. To compare the effectiveness of attribute and message features, we also trained classifiers using only attribute features, only message features, and both sets of features.

@@

\end{figure}
Figure \ref{git_comp} contains our accuracy results of every mined repository using one year of training data.  Results for random weighted coin vary but in general are about fifteen to twenty percentage points lower than the rest of the classifiers.  Using attribute features only tends to work as well or slightly better than message features, with big drops only occurring in cyclus and jquery, and scala.  Using both sets of features is comparable to only using attribute features.  Variation between data sets is comparable to the percentage bugginess in each training set, which is to be expected.

As encouraging as these initial results are, accuracy may not be the optimal way to view this data; as Table \ref{tab:buggy} shows, the  majority of our training and testing sets are less than 50 \% buggy.  A classifier could concievably classify all commits as clean, achieve > 50\% accuracy and be of no actual use finding buggy commits. In several instances, this is in fact what happens. The 93.3 \% accuracy seen by jedit is more than a little misleading; the jedit test set is only 6.7\% buggy, and so the jedit classifiers simply guess clean for every instance. This is the case for the majority of message-only feature classifiers; only cyclus and jquery  message-only classifiers ever classify any test commits as buggy.  The results from cyclus and jquery are still promisingly higher than our baseline, which leads us to believe that our features do have some non-random correlation with clean and buggy commits.   All of our attribute-trained and attribute/message-trained classifiers have non-trivial decision boundaries.  To get a better idea of how well our classifiers actually are at correctly predicting commits as buggy, we examine precision/recall graphs for cyclus, scala, and scipy by varying the ensemble classifier threshold from 0.0\% agreement (always classify buggy) to 100\% agreement in 10\% increments.  Precision (True Positives/(True Positives+False Positives) and Recall (True Positives/(True Positives+False Negatives)) seem like much more natural fits to analyze how well our ensemble classifiers are at classifying buggy commits.  We define buggy to be a positive and clean to be a negative. Intuitively, the farther up and to the right a point is, the better it performs at finding only true positives. We also provide some F-measure scores for the classifiers at various thresholds; the F-measure is the harmonic mean of precision and recall.  Assuming precision and recall are equally valued, a higher F-measure is an indication of better performance.

\begin{figure}[H]%
\centering
\subfloat[Cyclus]{\includegraphics[width=0.5\textwidth]{images/cyclus_pr_ann}}\hfill%
\subfloat[Scala]{\includegraphics[width=0.5\textwidth]{images/scala_pr_ann}}\\
\subfloat[Scipy]{\includegraphics[width=0.5\textwidth]{images/scipy_pr_ann}}\hfill
\subfloat[Cyclus - ROC graph]{\includegraphics[width=0.5\textwidth]{images/cyclus_roc}}\hfill

@@

As these figures show, using only comments can perform better than random, though not always without tuning of the threshold value.  While at the default 50\% threshold, Cyclus has a lower F-measure value than the random weighted coin, the threshold can can be tweaked to perform better. Scala performs better than average by default using message features than the random weighted coin. At the same time, using just comments performs noticeably worse in all cases than using attribute data.  In every case we examined, attribute data outperforms comment data at all thresholds. Using attribute data performs about as well as training on both attribute and comment features, though attribute-only classifiers consistently contained the maximum F-measure.  These results leads us to several conclusions.  First, both sets of attribute and comment features are more predictive than random.  Comparatively, attribute features are a much better approximation of a commit then comment features.  Combining attribute and comment features provide  little additional performance benefit over simply using attributes; with our current set of features, we gain do not gain substantive information from message features we did not already know from attribute features.

@@

 \begin{figure}[h]
\centering
	\subfloat[Accuracy]{\includegraphics[width=0.5\textwidth,height=0.3\textwidth]{images/time_comp}\hfill
	\label{time_comp:acc}}
	\subfloat[Precision Recall Graph- Puppet]{\includegraphics[width=0.5\textwidth]{images/time_pr_ann}\hfill
	\label{time_comp:pr}}
\caption{Training Data Size - Message and Attributes}
\label{time_comp}

\end{figure}
Another aspect of commits we wanted to look at is the size of the training set; is there a benefit to using older commits, or do they simply increase the noise in the data? If results are similar for a few months and the entire commit history, our classifier can be trained an order of magnitude faster with only a few months data.  The accuracy of each classifier from six months to the beginning of the repository can be found in figure \ref{time_comp:acc}. Accuracy across repositories tended to trend slightly downward as the time frame from the training set increased.  Not visible in table \ref{tab:buggy} is the fact that for six months data sets, the likelihood  of trivial decision boundaries increases.  On the other end of the spectrum, however,  using all the commit history seems to degrade results, possibly from overfitting.  Some of these projects predate git and almost certainly were originally in another version system.  Looking more in depth, we examined the Precision Recall graph for Puppet in \ref{time_comp:pr}.  All time frames perform similarly, for smaller thresholds, with a very strong downward trend for the entire commit history approaching 100\%. This would seem to imply that overfitting with all history only really becomes a problem when we force a large majority of the individual classifiers to agree.  But it appears from the data that there is no real benefit from using more data, which takes much longer to train.

Overall, it seems likely to us that recent commits are more representative of commits in the near future, which would explain the lack of change as we increase the size of the training set.  If older commits contained more valuable information or significantly distorted the results, we would see the drop off in all results.   From our work, we suspect six months to 1 year is the “optimal” range of training data, though this will obviously be different for each repository, depending on how often they make commits.

@@

A year of repository data before being able to use a tool seems like a high price of admission.  Being able to substitute another repository’s history for your own with little to no hit in performance would make a bug prediction tool more applicable.  Furthermore, what does this say about commits if commits from two unrelated repositories are similar enough that one can be used to train the other?  To answer these questions, we decided to  scipy and git to train our classifier and test on the other repositories.  Scipy and git were chosen because they were large repositories with good performance and non trivial decision boundaries.  In order for training and testing data to be compatible, the user feature had to be removed from all data sets.

 \begin{figure}[h]
\centering
	\subfloat[Accuracy]{\includegraphics[width=0.5\textwidth,height=0.3\textwidth]{images/git_comp}}
	\subfloat[Precision Recall-Puppet]{\includegraphics[width=.5\textwidth]{images/git_pr} \label{comp:pr}}
\caption{Training With Git and Scipy - 1 Months, Message and Attribute Data}
\label{git_comp}

@@

In general, results tended to be comparable to those using their respective data sets.  This comparable performance indicates to us that using a classifier trained on another repository is a valid proxy for repositories that do not have their own history.  It also seems that the distribution of message and commit attribute features we use do not vary much across repositories.  More work would need to be done to give such a claim actual weight, but if our features have global, general boundaries, could we use this information in some kind of prescriptive fashion, a la “keep your commits to X lines added if possible”. Or would knowledge and enforcement of this information simply shift the boundary?

\section{Threats to Validity}
\label{threats}

@@

Our results have shown commits are not especially repository specific, but we believe they could potentially be user-specific?  Does it make more sense to have a user-specific classifier that examines the user’s commit history across the repositories they have contributed to than to have a single classifier that predicts labels for potentially many users. Studying this would not require much additional new work to be done beyond mining new repositories and organizing training sets.  If user-specific commits are in fact better predictors of bugginess, additional work would need to be done to ensure user’s do not cherry-pick their training data to give an overly positive but invalid bias.

We could have looked at varying the size of the testing set, or the distance between the end of the training set and the beginning of the test set to examine how often retraining would need to take place; a classifier that takes twelve hours to train itself every six months to maintain performance is a much different prospect than having to retrain it every few days.  This information would be of great practical use to users and might also give us a better idea of which commits have the most impact on the decision boundaries.

@@

\section{Concluding Remarks}
\label{conclude}
The bugginess of commit messages can be predicted with some level of accuracy.  Commit messages also have some predictive information, though our current selection of message features performs worse than attribute features.  Because buggy commits are often significantly less common than clean commits, our classifiers run the risk of potentially creating trivial classifiers that only predict clean.  In practice, none of our attribute-feature-based classifiers experienced this, but several message-feature-based classifiers ran into this issue. Training using both attribute features and message features shows negligible benefit over training using only attribute features. After six months to a year, training on additional commits shows no performance boost and may in fact degrade results.  We have shown that classifiers trained on one repository can be used to successfully predict the bugginess of commits from another repository with little-to-no degradation of performance.   
% references section
